responseToFrankeTypicalUse...

### 2016-01-20 models/midScalarInvestigation.Rmd
two approaches to saliences with output to csv.

d = d %>% 
  gather(base, alt, 
         palatable, liked, good, loved, some, all, 
         delicious, excellent, memorable, unforgettable) %>%
  mutate(base = as.character(base)) %>%
  rowwise %>%
  mutate(scale = ifelse(base == "some" | base == "all", "some_all", 
                        ifelse(base == "palatable" | base == "delicious", "palatable_delicious",
                               ifelse(base == "liked" | base == "loved", "liked_loved",
                                      ifelse(base == "good" | base == "excellent", 
                                             "good_excellent", "memorable_unforgettable"))))) %>%
  group_by(scale, alt) %>%
  summarise(n = n())

# Plot findings of salient alternatives for each scale
# -------------------------------------------------------
scales = unique(d$scale)
ggplot(data=d[d$scale==scales[1],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 60) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[1])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(data=d[d$scale==scales[2],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 60) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[2])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(data=d[d$scale==scales[3],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 60) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[3])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(data=d[d$scale==scales[4],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 60) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[4])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(data=d[d$scale==scales[5],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 60) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[5])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

@@

```{r}
d <- fromJSON("../analysis/edited_alts.json", simplifyDataFrame=T) %>% as.data.frame(., stingasFactors = FALSE)

@@

saliences <- data.frame(scale = c(rep(scales[1], 5),
                                  rep(scales[2], 5),
                                  rep(scales[3], 5),
                                  rep(scales[4], 5),
                                  rep(scales[5], 5)),
                        degree = rep(degrees, 5),
#                                   rep(degrees[2], 5),
#                                   rep(degrees[3], 5),
#                                   rep(degrees[4], 5),
#                                   rep(degrees[5], 5)),
                        salienceCost = rep(NA, 5^2),
                        stringsAsFactors = FALSE)

# subset(altCounts, scale == "good_excellent" & Var1 == "amazing")$percent
# mapply(saliences$scale, saliences$degree, FUN = function(s, d) {
#   subset(altCounts, scale == s & degree == d)$percent
# })

# Saliency

# good_excellent
saliences[saliences$scale == "good_excellent",]$salienceCost <- c(1, 1, 0.022, 0.189, 0.089)
saliences[saliences$scale == "liked_loved",]$salienceCost <- c(1, 1, 0.0056, 0.25, 0.28)
saliences[saliences$scale == "palatable_delicious",]$salienceCost <- c(1, 1, 0.011, 0.089, 0.133)
saliences[saliences$scale == "memorable_unforgettable",]$salienceCost <- c(1, 1, 0.0389, 0.0722, 0.022)
saliences[saliences$scale == "some_all",]$salienceCost <- c(1, 0.1278, 1, 0.09444, 0.2167)
write.csv(saliences, file="saliences.csv")

currScale = "some_all"
subset(altCounts, scale == currScale & Var1 %in% topAlts[, currScale])
```

>>>>

d = d %>% 
  gather(base, alt, 
         palatable, liked, good, loved, some, all, 
         delicious, excellent, memorable, unforgettable) %>%
  mutate(base = as.character(base)) %>%
  rowwise %>%
  mutate(scale = ifelse(base == "some" | base == "all", "some_all", 
                        ifelse(base == "palatable" | base == "delicious", "palatable_delicious",
                               ifelse(base == "liked" | base == "loved", "liked_loved",
                                      ifelse(base == "good" | base == "excellent", 
                                             "good_excellent", "memorable_unforgettable"))))) %>%
  group_by(scale, alt) %>%
  summarise(n = n())
# write.csv(d, "e9_alternativeCounts.csv")
# Plot findings of salient alternatives for each scale
# -------------------------------------------------------
scales = unique(d$scale)
ggplot(data=d[d$scale==scales[1],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 60) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[1])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(data=d[d$scale==scales[2],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 60) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[2])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(data=d[d$scale==scales[3],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 60) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[3])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(data=d[d$scale==scales[4],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 60) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[4])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(data=d[d$scale==scales[5],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 60) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[5])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

@@

```{r}
d <- fromJSON("../analysis/edited_alts.json", simplifyDataFrame = TRUE) %>%
  as.data.frame(., stingasFactors = FALSE)

@@

saliences <- data.frame(scale = c(rep(scales[1], 5),
                                  rep(scales[2], 5),
                                  rep(scales[3], 5),
                                  rep(scales[4], 5),
                                  rep(scales[5], 5)),
                        degree = rep(degrees, 5),
                        salienceCost = rep(NA, 5^2),
                        stringsAsFactors = FALSE)

# Manual coding salience costs
saliences[saliences$scale == "good_excellent",]$salienceCost <- c(1, 1, 0.022, 0.189, 0.089)
saliences[saliences$scale == "liked_loved",]$salienceCost <- c(1, 1, 0.0056, 0.25, 0.28)
saliences[saliences$scale == "palatable_delicious",]$salienceCost <- c(1, 1, 0.011, 0.089, 0.133)
saliences[saliences$scale == "memorable_unforgettable",]$salienceCost <- c(1, 1, 0.0389, 0.0722, 0.022)
saliences[saliences$scale == "some_all",]$salienceCost <- c(1, 0.1278, 1, 0.09444, 0.2167)
# write.csv(saliences, file="saliences.csv")
```

Saliences as counts for primary scalars and participant responses
```{r}
d <- fromJSON("../analysis/edited_alts.json", simplifyDataFrame = TRUE) %>%
  as.data.frame(., stingasFactors = FALSE)
scales <- c("good_excellent",
            "liked_loved",
            "palatable_delicious",
            "memorable_unforgettable",
            "some_all")
degrees <- c("hi1", "hi2", "mid", "low1", "low2")

# Populate counts
altCounts <- data.frame(Var1 = c(), Freq = c(), NewFreq = c(), percent = c())
for (s in scales) {
  scaleHeads <- strsplit(s, "_")[[1]]
  s1 <- scaleHeads[1]
  s2 <- scaleHeads[2]
  combinedDf <- rbind(as.data.frame(table(d[, s1])), as.data.frame(table(d[, s2]))) %>%
    aggregate(Freq ~ Var1 ,data = ., FUN = sum) %>%
    mutate(scale = s,
           NewFreq = ifelse((Var1 == s1 | Var1 == s2), Freq + 90, Freq))

  altCounts <- rbind(altCounts, combinedDf)
}
#Adding 'palatable' to altCounts!!!
altCounts <- rbind(altCounts, data.frame(Var1 = "palatable", Freq = 0, scale = "palatable_delicious", NewFreq = 90))

# Populate saliences data for output
saliences <- data.frame(scale = c(), degree = c(), count = c(), newCount = c())
# good_excellent
saliences <- rbind(saliences,
      data.frame(scale = rep("good_excellent", 5), degree = degrees,
                 count = c(subset(altCounts, scale == "good_excellent" & Var1 == "excellent")$Freq,
                           subset(altCounts, scale == "good_excellent" & Var1 == "good")$Freq,
                           subset(altCounts, scale == "good_excellent" & Var1 == "okay")$Freq,
                           subset(altCounts, scale == "good_excellent" & Var1 == "bad")$Freq,
                           subset(altCounts, scale == "good_excellent" & Var1 == "horrible")$Freq),
                 newCount = c(subset(altCounts, scale == "good_excellent" & Var1 == "excellent")$NewFreq,
                           subset(altCounts, scale == "good_excellent" & Var1 == "good")$NewFreq,
                           subset(altCounts, scale == "good_excellent" & Var1 == "okay")$NewFreq,
                           subset(altCounts, scale == "good_excellent" & Var1 == "bad")$NewFreq,
                           subset(altCounts, scale == "good_excellent" & Var1 == "horrible")$NewFreq),
                 stringsAsFactors = FALSE))
# liked_loved
saliences <- rbind(saliences,
      data.frame(scale = rep("liked_loved", 5), degree = degrees,
                 count = c(subset(altCounts, scale == "liked_loved" & Var1 == "loved")$Freq,
                           subset(altCounts, scale == "liked_loved" & Var1 == "liked")$Freq,
                           subset(altCounts, scale == "liked_loved" & Var1 == "indifferent")$Freq,
                           subset(altCounts, scale == "liked_loved" & Var1 == "disliked")$Freq,
                           subset(altCounts, scale == "liked_loved" & Var1 == "hated")$Freq),
                 newCount = c(subset(altCounts, scale == "liked_loved" & Var1 == "loved")$NewFreq,
                           subset(altCounts, scale == "liked_loved" & Var1 == "liked")$NewFreq,
                           subset(altCounts, scale == "liked_loved" & Var1 == "indifferent")$NewFreq,
                           subset(altCounts, scale == "liked_loved" & Var1 == "disliked")$NewFreq,
                           subset(altCounts, scale == "liked_loved" & Var1 == "hated")$NewFreq),
                 stringsAsFactors = FALSE))
# memorable_unforgettable
saliences <- rbind(saliences,
      data.frame(scale = rep("memorable_unforgettable", 5), degree = degrees,
                 count = c(subset(altCounts, scale == "memorable_unforgettable" & Var1 == "unforgettable")$Freq,
                           subset(altCounts, scale == "memorable_unforgettable" & Var1 == "memorable")$Freq,
                           subset(altCounts, scale == "memorable_unforgettable" & Var1 == "ordinary")$Freq,
                           subset(altCounts, scale == "memorable_unforgettable" & Var1 == "bland")$Freq,
                           subset(altCounts, scale == "memorable_unforgettable" & Var1 == "forgettable")$Freq),
                 newCount = c(subset(altCounts, scale == "memorable_unforgettable" & Var1 == "unforgettable")$NewFreq,
                           subset(altCounts, scale == "memorable_unforgettable" & Var1 == "memorable")$NewFreq,
                           subset(altCounts, scale == "memorable_unforgettable" & Var1 == "ordinary")$NewFreq,
                           subset(altCounts, scale == "memorable_unforgettable" & Var1 == "bland")$NewFreq,
                           subset(altCounts, scale == "memorable_unforgettable" & Var1 == "forgettable")$NewFreq),
                 stringsAsFactors = FALSE))

# palatable_delicious
saliences <- rbind(saliences,
      data.frame(scale = rep("palatable_delicious", 5), degree = degrees,
                 count = c(subset(altCounts, scale == "palatable_delicious" & Var1 == "delicious")$Freq,
                           subset(altCounts, scale == "palatable_delicious" & Var1 == "palatable")$Freq,
                           subset(altCounts, scale == "palatable_delicious" & Var1 == "mediocre")$Freq,
                           subset(altCounts, scale == "palatable_delicious" & Var1 == "gross")$Freq,
                           subset(altCounts, scale == "palatable_delicious" & Var1 == "disgusting")$Freq),
                 newCount = c(subset(altCounts, scale == "palatable_delicious" & Var1 == "delicious")$NewFreq,
                           subset(altCounts, scale == "palatable_delicious" & Var1 == "palatable")$NewFreq,
                           subset(altCounts, scale == "palatable_delicious" & Var1 == "mediocre")$NewFreq,
                           subset(altCounts, scale == "palatable_delicious" & Var1 == "gross")$NewFreq,
                           subset(altCounts, scale == "palatable_delicious" & Var1 == "disgusting")$NewFreq),
                 stringsAsFactors = FALSE))

# some_all
saliences <- rbind(saliences,
      data.frame(scale = rep("some_all", 5), degree = degrees,
                 count = c(subset(altCounts, scale == "some_all" & Var1 == "all")$Freq,
                           subset(altCounts, scale == "some_all" & Var1 == "most")$Freq,
                           subset(altCounts, scale == "some_all" & Var1 == "some")$Freq,
                           subset(altCounts, scale == "some_all" & Var1 == "little")$Freq,
                           subset(altCounts, scale == "some_all" & Var1 == "none")$Freq),
                 newCount = c(subset(altCounts, scale == "some_all" & Var1 == "all")$NewFreq,
                           subset(altCounts, scale == "some_all" & Var1 == "most")$NewFreq,
                           subset(altCounts, scale == "some_all" & Var1 == "some")$NewFreq,
                           subset(altCounts, scale == "some_all" & Var1 == "little")$NewFreq,
                           subset(altCounts, scale == "some_all" & Var1 == "none")$NewFreq),
                 stringsAsFactors = FALSE))

# write.csv(saliences, "model_data/saliences5.csv")
```
